Probabilites of polar aligned disks in binary star systems

### 2024-02-20 src/tex/ms.tex
Start the introduction

>>>>

[\textcolor{red}{Why?}]

Circumbinary planets -- those orbiting two stars -- have been mostly found to orbit in the same plane as
their hosts \citep{2011Sci...333.1602D,2012ApJ...758...87O,2012Natur.481..475W}. However, \citet{2023ApJ...957L..28M}
found evidence for a circumbinary planet that orbits nearly perpendicular to the binary orbinal plane.
